EIP CRE transmission network manuscript figures and data

### 2022-09-13 manuscript-figures.Rmd
Fix order of fig 4 y axis

tn_facil_hm <- prior_hosps_tn_counts %>% 
  mutate(Facility = factor(Facility, levels = rev(tn_hm$tree_col$labels[tn_hm$tree_col$order]) %>% gsub('TDH.', 'TDH-', .) %>% gsub('LONG.', 'LONG-', .) %>% gsub('VA.', 'VA-', .) %>% gsub('\\.', ' ', .)),
         ST = factor(ST, levels = tn_hm$tree_row$labels),
         ST = gsub('E. hormaechei', '*E. hormaechei*', ST),
         ST = gsub('K. pneumoniae', '*K. pneumoniae*', ST)) %>% 
  ggplot(aes(x = Facility, y = ST, fill = count)) +
  geom_tile() +
  geom_rect(aes(xmin = 0+0.5, xmax = 7+0.5, ymin = 0+0.5, ymax = 3+0.5), fill = NA, col = 'black', size = 1, linetype = 'dotted') +
  scale_fill_viridis_c(direction = -1, breaks = scales::pretty_breaks(), option = 'magma') +
  theme_classic() +
  theme(axis.text.x = element_blank(), axis.text.y = element_markdown()) +
  labs(fill = 'Count')

>>>>

tn_facil_hm <- prior_hosps_tn_counts %>% 
  mutate(Facility = factor(Facility, levels = rev(tn_hm$tree_col$labels[tn_hm$tree_col$order]) %>% gsub('TDH.', 'TDH-', .) %>% gsub('LONG.', 'LONG-', .) %>% gsub('VA.', 'VA-', .) %>% gsub('\\.', ' ', .)),
         ST = factor(ST, levels = tn_hm$tree_row$labels),
         ST = gsub('E. hormaechei', '*E. hormaechei*', ST),
         ST = gsub('K. pneumoniae', '*K. pneumoniae*', ST), 
         ST = factor(ST, levels = rev(c('*K. pneumoniae* ST258', '*E. hormaechei* ST171', 'Other', '*E. hormaechei* ST114', '*K. pneumoniae* ST307'))),

  ggplot(aes(x = Facility, y = ST, fill = count)) +
  geom_tile() +
  geom_rect(aes(xmin = 0+0.5, xmax = 7+0.5, ymin = 0+0.5, ymax = 3+0.5), fill = NA, col = 'black', size = 1, linetype = 'dotted') +
  scale_fill_viridis_c(direction = -1, breaks = scales::pretty_breaks(), option = 'magma') +
  theme_classic() +
  theme(axis.text.x = element_blank(), axis.text.y = element_markdown()) +
  labs(fill = 'Count')
